---
title: "GH Projct2 Doctors Donot travel"
author: "Hui (Gracie) Han"
date: "October 7, 2018"
output: html_document
---

Purpose:
1) choose the dataset of "Doctors who do not travel", which was identified by other student in the week5 discussion
2) Read the information from csv file into R
3)this dataset is in a long format (the location of doctors who travel are in their own row), need to be spread into wide format
4) some varibles are not needed, so we get rid of it
5) Do some plots for data visulization
 6) Research qeustion: 

```{r}
# file name: GH Project2 Doctors Who Do not travel 

getwd()

setwd('D:/Project2 Week6 Due Oct7 GH DataToUse')

```

```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(sqldf)
library(magrittr)
library(DT)
```

```{r}
dataraw2 <- read.csv ("D:/Project2 Week6 Due Oct7 GH DataToUse/Doctor Who Time Travel Journeys.csv")
print(dataraw2)
```
to select only the needed column, to get rid of the columnn not needed, 
```{r}
Data11 <- dataraw2 %>% 
  select (c (Doctor.Who.season, doctor.actor,ep..no,from,estimated.from,
    planet,sub.location, location)
    )
summary (Data11)
head(Data11)
tail(Data11)
```
```{r}
# get rid of row 98, because it is exactly the same as row 59, which causes problem in the spread function downstream
#Error: Duplicate identifiers for rows (59, 98), this error was fixed in the earlier block, otherwise this  block will not run
Data31 <- Data11 [-98,]
print (Data31)
```
Tospread the data Iit is in the long format, need to be transformed into wide format), and eleimnate the col nont needed
```{r}


Data51 <- 
  Data31 %>% 
  spread(planet,sub.location ) %>% 

 group_by(from)  %>% 
   arrange(from)
# this (from) variable is the year variable

summary (Data51)
 head(Data51)
 tail(Data51)
 #print(Data51)
 
```
```{r}
write.csv (Data11,'Data51DoctorsWhoTravel.csv')
# this is 135*6 dimension table,
```

```{r}
# Analyse the data by season of the show
Data71 <- Data51 %>%
  group_by (Doctor.Who.season)
head(Data71)
tail (Data71)
print(Data71)
```{
```
  
```

```{r}
write.csv (Data71,'Data71DoctorsWhoTravel.csv')
# this is 135 * 17 dimention
```
