---
title: "Project 2 NYPD Motoris Collision"
author: "Hui (Gracie) Han"
date: "October 8, 2018"
output: html_document
---
```{r}
getwd()
setwd('D:/Project2 Week6 Due Oct7 GH DataToUse')
```



```{r}
library(tidyr)
library(dplyr)
```

```{r}
NYPDCollision <- tbl_df(read.csv("NYPDAug2017_Motor_Vehicle_Collisions.csv", stringsAsFactors = FALSE, check.names = FALSE))

head(NYPDCollision)
tail(NYPDCollision)
```

```{r}
NYPDCollision.ByInjuryType2 <- NYPDCollision %>% 
gather(InJury_type,NofCases, c("Number_of_Motor_Vehicle_Collisions", "Vehicles_or_Motorists_Involved", "Injury_or_Fatal_Collisions","MotoristsInjured","MotoristsKilled","PassengInjured","CyclistsInjured",
"CyclistsKilled","PedestrInjured","PedestrKilled","Bicycle" ))

head(NYPDCollision.ByInjuryType2)
tail(NYPDCollision.ByInjuryType2)
```
Find the Min N of cases, and the Maximum N of cases, by Injury Type 
```{r}
NYPDCollision.ByInjuryType_Max <- NYPDCollision.ByInjuryType2 %>% 
  group_by(InJury_type) %>% 
  arrange(-NofCases) %>%
  filter(row_number()==1)

NYPDCollision.ByInjuryType_Min <- NYPDCollision.ByInjuryType2 %>% 
  group_by(InJury_type) %>% arrange(NofCases) %>%
  filter(row_number()==1)

(NYPDCollision.ByInjuryType_Max)
(NYPDCollision.ByInjuryType_Min)
```

To Examine the highest collion rate by location of Boro
```{r}
NYPDCollision.ByBoro_Max2 <- NYPDCollision.ByInjuryType2 %>% 
  group_by(Boro_Location) %>% 
  arrange(-NofCases) %>%
  filter(row_number()==1)

(NYPDCollision.ByBoro_Max2)
```
write a csv file for data visulization
```{r}
write.csv(NYPDCollision.ByBoro_Max2, 'NYPDCollisionByBoro_Max.csv')
```
conclusion from above analysis: the maximum number of cases (1248 cases) occured in the Queens 109th Precint


Find the Max N of cases, by the location and the Injury Type 
```{r}
NYPDCollision.ByBoroInjuryType_Max3 <- NYPDCollision.ByInjuryType2 %>% 
  group_by(Boro_Location, InJury_type) %>% 
  arrange(-NofCases) %>%
  filter(row_number()==1)

(NYPDCollision.ByBoroInjuryType_Max3)

```
write a csv file for data visulization

```{r}
write.csv(NYPDCollision.ByBoroInjuryType_Max3, 'NYPDCollisionByBoroInjuryType_Max.csv')
```
conclusion from above analysis: the maximum number of cases (1248 cases) occured in the Queens 109th Precint, with the most injury type as 'Vehicles_or_Motorists_Involved'
